\section{Compiler Technique}
\begin{definition}[LL]\label{def:LL}
\end{definition}

\begin{definition}[Control Stack]\label{def:staticmemory}
    Where procedure calls and returns go. Each function typically has
    its own frame. We call such a frame for a funciton an activation record.
\end{definition}

\begin{definition}[Live Variable]\label{def:livevariable}
    A variable which holds a value that might be read. If a value is assigned
    to but never used again it is not in the out-set of a block in a control
    flow graph.
\end{definition}

\begin{definition}[Static Memory]\label{def:staticmemory}
    Where globals and metadata for programs go.
\end{definition}

\begin{definition}[Static Memory]\label{def:staticmemory}
    Where globals and metadata for programs go. Static is always known at
    compile time.
\end{definition}

\subsubsection{notes}
If you can construct a table with FIRST and FOLLOW and there are no
conflicts, grammar is $LL(1)$. That is, for a nonterminal, $FIRST(\alpha) \cap FIRST(\beta) = \emptyset$, for any pair of production-rules $\alpha$ and $\beta$ where the leftmost-derivation is different (i.e., they do not result in the same string). If any production rule $\alpha$ A $\xRightarrow{*} \epsilon$, then the rule extends such that $FIRST(A) \cap FOLLOW(A) = \emptyset$
\usepackage{mathtools}
TODO: predictive parser construction (not learning is ill advised)
TODO: $LR(1)$ vs SLR vs LALR
TODO: what happens if you increase the lookahead for a given parser?
TODO: more shift/reduce \dots what is shift-shift vs reduce-reduce?
TODO: design a proof tree
TODO: semantic tree (?)
TODO: consumption: can CFG express CFG? 

TODO: halting problem? mentioned in slide\dots

TODO: can regex be recognized by regex, DFA or NFA?
TODO: dispatch vectors, especially with multiple inheritance
    how are interfaces vs class inheritance?
TODO: exam 2008; optimize code
TODO: review PS{1,2,3,4,5,6}
TODO: can pointers do GC?
TODO: heap memory fragmentation?.
TODO: process image? (draw it?)
TODO: meet over paths? (if relevant)
TODO: live variable (how many live at return is possible?)
TODO: monotonicity of transfer functions, why is this useful?
    distributivity?
TODO: what difference does it make to have external or language-dependent feature?
TODO: static, strong typing?
TOOD: syntax tree?
TODO: tiling and instructions?
TODO: review PS6 in regards to assembly (push bsp or bbp?)
TODO: write down the dangling else fixup
