\section{Graphs}

\begin{definition}[Arborescence]
    an arborescence is a directed graph in which, for a vertex u called the
    root and any other vertex v, there is exactly one directed path from u to v.
 \end{definition}

\begin{definition}[Clique]
    A subset of vertices $C \subset V$, such that in this subgraph all nodes
    are connected, i.e.\ there is an edge from every pair of nodes.
\end{definition}

\begin{definition}[Connected graph (component)]\label{connectedcomp}
    A graph in which, from any $v \in V$, you can reach any other $u \neq v$
\end{definition}

\begin{definition}[Directed graph]
    Properties:
    \begin{itemize}
        \item $\sum\limits_{v \in V}{d(v)} = 2|E|$
        \item $\sum\limits_{v \in V}{indegree(v)} = 
            \sum\limits_{v \in V}{outdegree(v)}$
    \end{itemize}
\end{definition}

\begin{definition}[Eularian]\label{eularian}
    Visit each \textit{edge} once.
\end{definition}

\begin{definition}[Hamiltonian]
    Visit each \textit{vertex} once.
\end{definition}

\begin{definition}[Metric spaces]\label{metric}
    See also~\nameref{semimetric}
    Properties:
    \begin{itemize}
        \item $d_{u,v} = 0 \iff u = v$
        \item $d_{u,v} = d_{v,u}$
        \item $\forall k, d_{u,v} \leq d_{u,k} + d_{k,v}$
    \end{itemize}
\end{definition}

\begin{definition}[Minimum mean cost]
    minimize ratio of cost of arcs (directed edges) to number of arcs
\end{definition}

\begin{definition}[MST]
    A mininum~\nameref{spantree}, such the weight of this tree is less than
    or equal to all other possible~\nameref{spantree}.
\end{definition}

\begin{definition}[Planar graph]
    No edges need to cross each other.
\end{definition}

\begin{definition}[Semi-metric]\label{semimetric}
    Like a~\nameref{metric}, without the property that
    $d_{u,v} = 0 \iff u = v$
\end{definition}


\begin{definition}[Spanning tree]\label{spantree}
    Connected, undriected graph that has all vertices and some subset
    of edges to form a tree.
\end{definition}

\begin{definition}[Strongly connected component]
    Similar to~\nameref{connectedcomp}, but in a directed graph.
\end{definition}

\begin{definition}[Topological sort]\label{topsort}
    Runs in O(V + E), same as DFS, although it can be supered to $O(\log_{2} n)$
\end{definition}

\begin{definition}[Tree]\label{tree}
    Properties of a tree:
    \begin{itemize}
        \item in a tree, there will always be an even amount of nodes that has
            an uneven degree.
        \item Degree of nodes in a tree is at most twice the number of nodes
    \end{itemize}
\end{definition}



\begin{definition}[Vertex-cover]
    A selection of vertices such that each edge is incident to at least one
    of them.
\end{definition}

